---
# Report details
title: "`r paste('Progress report for project', params[['project-number']])`"
subtitle: "Subtitle Here"
params:
  uni: CU
  pri_bio: Your.Name
  project-number: ABC1234-567XYZ
  partner: collab_partner
  partner_email: colla_partner@email.com.au
bibliography: references.bib
date: last-modified
version-number: 1.0.0
format: aagi-pdf+short+report
---

```{r}
#| include: false
#| label: setup
# This is probably necessary on Linux (with Proxima Nova and Cairo
# installed). We may need something else on Mac.
if (toupper(Sys.info()["sysname"]) == "LINUX" ||
  toupper(Sys.info()["sysname"]) == "DARWIN") {
  knitr::opts_chunk$set(dev = c("cairo_pdf"))
}

if (require(xtable)) {
  options(xtable.comment = FALSE)
}
if (require(formatR)) {
  options(formatR.arrow = FALSE)
  knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 60)
  )
}

if (!require(pak)) {
  install.packages("pak", dependencies = TRUE)
}
if (!require(flextable)) {
  pak::pak("flextable", dependencies = TRUE)
}
# Integrating with AAGIPalettes, AAGIThemes
if (!require(AAGIThemes)) {
install.packages("AAGIThemes",
                 repos = c("https://aagi-aus.r-universe.dev",
                           "https://cloud.r-project.org"))
}
if (!require(AAGIPalettes)) {
install.packages("AAGIPalettes",
                 repos = c("https://aagi-aus.r-universe.dev",
                           "https://cloud.r-project.org"))
}

library(flextable)
library(AAGIThemes)
library(AAGIPalettes)
library(ggplot2)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(theme_fun = theme_ft_aagi)
```

```{r}
#| include: false
#| label: config-for-title

if(params$uni == "CU"){
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
  email = "cbada@curtin.edu.au"
} else if(params$uni == "UA"){
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
  email = paste(params$pri_bio, "adelaide.edu.au", sep = "")
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
  email = paste(params$pri_bio, "@uq.edu.au", sep = "")
}
```

---
author:
  - "Prepared for: `r params$partner` (`r params$partner_email`)"
  - "Prepared by: `r params$pri_bio`, Author 2"
  - "Project Lead: `r project_lead`"
email: "`r email`"
---

# Section 1

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc using the various AAGI palette colours. Use `\textcolor{aagiteal}{...}` for `\textcolor{aagiteal}{AAGI Teal}`, or `\textcolor{aagibrightgreen}{...}` for `\textcolor{aagibrightgreen}{AAGI Bright Green}`, for instance. @tbl-aagipalette shows the standard palette colours available for use.

::: {#tbl-aagipalette}
  \centering
  \begin{tabular}{|c | c | c | c |}
    \hline
    \cellcolor{aagibrightgreen}\texttt{aagibrightgreen} & %
    \cellcolor{aagiteal}\color{white}\texttt{aagiteal} & %
    \cellcolor{aagiblue}\texttt{aagiblue} & %
    \cellcolor{aagigreen}\texttt{aagigreen} \\
    \hline
    \cellcolor{aagiyellow}\texttt{aagiyellow} & %
    \cellcolor{aagiorange}\texttt{aagiorange} & %
    \cellcolor{aagiblack}\color{white}\texttt{aagiblack} & %
    \cellcolor{aagigrey}\texttt{aagigrey} \\
    \hline
  \end{tabular} 

The AAGI palette colours.
:::

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

\begin{note}
  {\bf\color{aagiteal!75!black} Example Note}\quad
  Use \verb|\begin{note}...\end{note}| to create coloured notes like this
  that stand out on the page.
\end{note}

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

# Table example using {flextable}

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft

```


### This is a subsubsection heading

\lipsum[1-3]

And so on.

# Next Section

Add as many sections as needed.

# References
