---
# Report details
title: "`r paste('Progress report for project', params[['project-number']])`"
subtitle: "Subtitle here"
category: "`r paste(params[['project-number']])`"
params:
  uni: CU
  pri_bio: Your.Name
  project-number: ABC1234-567XYZ
  partner: collab_partner
  partner_email: collab_partner@email.com.au
bibliography: references.bib
date: last-modified
version-number: 1.0.0
format: aagi-docx+short+report
---

```{r setup}
#| include: false

if (toupper(Sys.info()["sysname"]) == "LINUX" ||
  toupper(Sys.info()["sysname"]) == "DARWIN") {
  knitr::opts_chunk$set(dev = c("cairo_pdf"))
}

if (require(xtable)) {
  options(xtable.comment = FALSE)
}
if (require(formatR)) {
  options(formatR.arrow = FALSE)
  knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 60)
  )
}

# Integrating with AAGIPalettes, AAGIThemes
if (!requireNamespace("pak", quietly = TRUE)) {
  install.packages("pak")
}
if (!require(AAGIThemes)) {
  pak::pkg_install(
    "AAGI-AUS/AAGIThemes",
    dependencies = TRUE, upgrade = FALSE
  )
}
if (!require(AAGIPalettes)) {
  pak::pkg_install(
    "AAGI-AUS/AAGIPalettes",
    dependencies = TRUE, upgrade = FALSE
  )
}
if (!require(flextable)) {
  install.packages("flextable")
}
library(AAGIThemes)
library(AAGIPalettes)
library(flextable)
```

```{r sp}
#| include: false
#| label: config-for-title

if(params$uni == "CU"){
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
  email = "cbada@curtin.edu.au"
} else if(params$uni == "UA"){
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
  email = paste(params$pri_bio, "adelaide.edu.au", sep = "")
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
  email = paste(params$pri_bio, "@uq.edu.au", sep = "")
}
```

---
author:
  - "Prepared for: `r params$partner` (`r params$partner_email`)"
  - "Prepared by: `r params$pri_bio`, Author 2"
  - "Project Lead: `r project_lead`"
  - "email: `r email`"
subject: "`r email`"
---

# Section 1

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

```{r}
#| label: tbl-example
#| tbl-cap: "Here is a table."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft

```

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r plot-eg}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

### This is a subsubsection heading

And so on.

# Next Section

Add as many sections as needed.

# References
