---
format:
  aagi-pdf+report
execute: 
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  uni: CU
  pri_bio: Your.Name
  project_num: AAA--BBB
bibliography: references.bib
editor: visual
---

```{r}
#| include: false
#| label: param_uni

if (params$uni == "CU") {
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
} else if (params$uni == "UA") {
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
}
```

```{r}
#| include: false
#| label: email for project lead

if (params$uni == "CU") {
  email = "cbada@curtin.edu.au"
} else if (params$uni == "UA") {
  email = paste(params$pri_bio, "@adelaide.edu.au", sep = "")
} else {
  email = paste(params$pri_bio, "@uq.edu.au")
}
```

```{r}
#| label: title param
#| include: false

if (params$uni == "CU") {
  university <- "Curtin University"
} else if (params$uni == "UA") {
  university <- "University of Adelaide"
} else {
  university <- "University of Queensland"
}

```

```{r}
#| label: Project number
#| include: false

Pro_Num = params$project_num
```

```{=latex}
%\begin{titlepage}

%\thispagestyle{Title_page}

%\vspace*{-2cm}

%  \begin{center}
%    \includegraphics[height=3cm]{assets/AAGI_logo.pdf}    
%  \end{center}

%  \vfill
  
%  \rule{\textwidth}{0.5pt}

%  \begin{FlushRight}

%    \Huge
%    \textcolor{aagiteal}{\textbf{Analytics for the Australian Grains Industry 
%      -\\ `r university` (AAGI-`r params$uni`)\\
%      Technical Report Series: 123}}\\[6mm]
      
%    \Large
%    {\textbf{Informative title for report}}\\
%    \vspace{2mm}{\textbf{Report for `r Pro_Num`}}\\[5mm]

%    \normalsize
%    \textbf{Your Name}\\
%    \vspace*{0.4cm}
%    \textbf{Email:}\; \texttt{%
%      \href{mailto:`r email`}%
%      {`r email`}}\\[8mm]
%    \textbf{Project Leads: `r project_lead`}\\[8mm]
      
%    \today
%  \end{FlushRight}
%  \rule{\textwidth}{0.5pt}
  
%  \vfill
  
%\end{titlepage}
```
---
title: "Analytics for the Australian Grains Industry - `r university` (AAGI-`r params$uni`)  \n Technical Report Series: 123"
subtitle: "Descriptive title for report  \n Report for `r Pro_Num`"
author: 
  - Adam Sparks
  - "Email: `r email`"
  - "Project Leads: `r project_lead`"
---

```{r}
#| label: load
#| message: false

library(ggplot2)
library(AAGIThemes)
library(flextable)
library(dplyr)

# set ggplot2 theme
theme_set(theme_aagi())
```

\newpage

```{=latex}
\clearpage
\setcounter{page}{1}
```
\tableofcontents

\newpage

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References

Cited works and literature. @Box1976

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
