---
# Report details
title: "`r paste('Progress report for project', params[['project-number']])`"
subtitle: "Subtitle here"
params:
  uni: CU
  pri_bio: Your.Name
  project-number: ABC1234-567XYZ
date: "`r format(Sys.time(), '%d %B, %Y')`"
version-number: 1.0.0
format: 
  aagi-pdf-short-report: default
---

```{r}
#| include: false

# library(rmarkdown)

# This is probably necessary on Linux (with Proxima Nova and Cairo
# installed). We may need something else on Mac.
if (toupper(Sys.info()["sysname"]) == "LINUX") {
  knitr::opts_chunk$set(dev = c("cairo_pdf"))
}

if (require(xtable)) {
  options(xtable.comment = FALSE)
}
if (require(formatR)) {
  options(formatR.arrow = FALSE)
  knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 60)
  )
}

# Integrating with AAGIPalettes, AAGIThemes
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
if (!require(AAGIThemes)) {
  remotes::install_github(
    "AAGI-AUS/AAGIThemes", dependencies = TRUE, upgrade = FALSE
  )
}
if (!require(AAGIPalettes)) {
  remotes::install_github(
    "AAGI-AUS/AAGIPalettes", dependencies = TRUE, upgrade = FALSE
  )
}
library(AAGIThemes)
library(AAGIPalettes)
```

```{r}
#| include: false
#| label: config-for-title

if(params$uni == "CU"){
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
  email = "cbada@curtin.edu.au"
} else if(params$uni == "UA"){
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
  email = paste(params$pri_bio, "adelaide.edu.au", sep = "")
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emertius Prof Kaye Basford"
  email = paste(params$pri_bio, "@uq.edu.au", sep = "")
}
```

---
author:
  - "`r params$pri_bio`"
  - Author 2
  - "Project Lead: `r project_lead`"
email: "`r email`"
---

# Section 1

Report text goes here. This template is designed for smaller ("one-page") AAGI
reports. The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc using the various AAGI palette colours. Use 
`\textcolor{aagiteal}{...}` for \textcolor{aagiteal}{AAGI Teal}, or 
`\textcolor{aagibrightgreen}{...}` for 
\textcolor{aagibrightgreen}{AAGI Bright Green}, for instance. @tbl-aagipalette shows the standard palette colours available for use.

::: {#tbl-aagipalette}
```{=tex}
  \centering
  \begin{tabular}{|c | c | c | c |}
    \hline
    \cellcolor{aagibrightgreen}\texttt{aagibrightgreen} & %
    \cellcolor{aagiteal}\color{white}\texttt{aagiteal} & %
    \cellcolor{aagiblue}\texttt{aagiblue} & %
    \cellcolor{aagigreen}\texttt{aagigreen} \\
    \hline
    \cellcolor{aagiyellow}\texttt{aagiyellow} & %
    \cellcolor{aagiorange}\texttt{aagiorange} & %
    \cellcolor{aagiblack}\color{white}\texttt{aagiblack} & %
    \cellcolor{aagigrey}\texttt{aagigrey} \\
    \hline
  \end{tabular} 
```

The AAGI palette colours.

:::


## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the
report by default, after the last heading `# References` on the last line of
this .Rmd file (but feel free to change the title to whatever you like).

\begin{note}
  {\bf\color{aagiteal!75!black} Example Note}\quad
  Use \verb|\begin{note}...\end{note}| to create coloured notes like this
  that stand out on the page.
\end{note}

Example R code, using the `AAGIThemes` package to produce 
Figure \@ref(fig:example1).
```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

### This is a subsubsection heading

\lipsum[1-3]

And so on.

# Next Section

Add as many sections as needed.

# References
