---
format:
  aagi-docx+report: default
execute: 
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
params:
  uni: CU
  pri_bio: Your.Name
  project_num: AAA--BBB
  partner: collab_partner
  partner_email: collab_partner@email.com.au
bibliography: references.bib
date: "`r Sys.Date()`"
date-format: long
---

```{r setup}
#| include: false

if (toupper(Sys.info()["sysname"]) == "LINUX" ||
  toupper(Sys.info()["sysname"]) == "DARWIN") {
  knitr::opts_chunk$set(dev = c("cairo_pdf"))
}

if (require(xtable)) {
  options(xtable.comment = FALSE)
}
if (require(formatR)) {
  options(formatR.arrow = FALSE)
  knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 60)
  )
}

# Integrating with AAGIPalettes, AAGIThemes
if (!requireNamespace("pak", quietly = TRUE)) {
  install.packages("pak")
}
if (!require(AAGIThemes)) {
  pak::pkg_install(
    "AAGI-AUS/AAGIThemes",
    dependencies = TRUE, upgrade = FALSE
  )
}
if (!require(AAGIPalettes)) {
  pak::pkg_install(
    "AAGI-AUS/AAGIPalettes",
    dependencies = TRUE, upgrade = FALSE
  )
}
if (!require(flextable)) {
  install.packages("flextable")
}
library(AAGIThemes)
library(AAGIPalettes)
library(flextable)
```

```{r university}
#| label: university
#| include: false

if (params$uni == "CU") {
  university <- "Curtin University"
} else if (params$uni == "UA") {
  university <- "University of Adelaide"
} else {
  university <- "University of Queensland"
}
```


```{r project-lead}
#| include: false
if (params$uni == "CU") {
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
} else if (params$uni == "UA") {
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
}
```

```{r lead-email}
#| include: false
#| label: email for project lead

if (params$uni == "CU") {
  email = "cbada@curtin.edu.au"
} else if (params$uni == "UA") {
  email = paste(params$pri_bio, "@adelaide.edu.au", sep = "")
} else {
  email = paste(params$pri_bio, "@uq.edu.au")
}
```

```{r project-number}
#| label: Project number
#| include: false

Pro_Num = params$project_num

```

---
title: "Analytics for the Australian Grains Industry - `r university` (AAGI-`r params$uni`)  \n Technical Report Series: 123"
subtitle: "Descriptive title for report  \n Report for `r Pro_Num`"
author:
  - "Prepared for: `r params$partner` (`r params$partner_email`)"
  - "Prepared by: `r params$pri_bio`"
  - "Project Lead: `r project_lead`"
  - "email: `r email`"
---

```{r}
#| label: load
#| message: false

library(ggplot2)
library(AAGIThemes)
library(flextable)
library(dplyr)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)
```

\newpage

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

ggplot(data = pressure, aes(x = temperature, 
                            y = pressure)) + 
  geom_point() +
  theme_aagi()

```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft

```

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References (Optional)

Cited works and literature. @Box1976

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
