---
title: "AAGI"
author: "Analytics for the Australian Grain Industry"
date: last-modified
format:
  aagi-pptx: default
---

```{r}
#| label: load
#| message: false

if (!require(pak)) {
  install.packages("pak", dependencies = TRUE)
}
if (!require(flextable)) {
  pak::pak("flextable", dependencies = TRUE)
}
if (!require(AAGIThemes)) {
  install.packages("AAGIThemes",
                 repos = c("https://aagi-aus.r-universe.dev",
                           "https://cloud.r-project.org"))
}
if (!require(AAGIPalettes)) {
  install.packages("AAGIPalettes",
                   repos = c("https://aagi-aus.r-universe.dev",
                             "https://cloud.r-project.org"))
}

if (!require("gapminder")) {
  install.packages("gapminder")
}

library(ggplot2)
library(AAGIThemes)

# set ggplot2 theme
theme_set(theme_aagi())
```

## An AAGI pptx Theme for Quarto

This Quarto extension allows you to create your slides using a theme that follows AAGI typography and colour styles and provides the official AAGI logo and cover image for the title slide.

## Bullet point

-   Point 1
-   Point 2

## Tables

For tables, we suggest paring with the R package [{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) to provide AAGI themed tables using `theme_ft_aagi`, that offers more flexibility in formatting.

## Example

```{r}
#| label: tab-AAGI
#| message: false
#| echo: false

library(dplyr)
library(flextable)
library(AAGIThemes)

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)

flex_tab <- flextable(head(airquality) |>
 mutate(`Month Name` = "May")) |>
  autofit()
flex_tab
```

## Basic Figures

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming basic figures in R, for example.

```{r}
#| label: graphics-figure
#| message: false
library(AAGIThemes)
plot_aagi(pressure)
```

## Figures with {ggplot2}

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming [{ggplot2}](https://ggplot2.tidyverse.org) outputs in R, for example.

```{r}
#| label: ggplot2-figure
#| message: false
#Prepare data

library(gapminder)
library(dplyr)
library(ggplot2)
library(AAGIThemes)

facet <- gapminder |>
  filter(continent != "Americas") |>
  group_by(continent, year) |>
  summarise(pop = sum(as.numeric(pop)))
#> `summarise()` has grouped output by 'continent'. You can override using the
#> `.groups` argument.

col_values <- c(
  AAGIPalettes::colour_as_hex("AAGI Teal"),
  AAGIPalettes::colour_as_hex("AAGI Green"),
  AAGIPalettes::colour_as_hex("AAGI Yellow"),
  AAGIPalettes::colour_as_hex("AAGI Blue")
)

#Make plot
ggplot() +
  geom_area(data = facet, aes(x = year, y = pop, fill = continent)) +
  scale_fill_manual(values = col_values) +
  facet_wrap(~ continent, ncol = 5) +
  scale_y_continuous(breaks = c(0, 2000000000, 4000000000),
                    labels = c(0, "2bn", "4bn")) +
  theme_aagi() +
  geom_hline(yintercept = 0,
            linewidth = 1,
            colour = "#474747") +
  theme(legend.position = "none", axis.text.x = element_blank()) +
  labs(title = "Asia's rapid growth", subtitle = "Population growth by continent, 1952-2007")
```

## Slides With Columns

::::: columns
::: {.column width="50%"}
This is a column on the left.
:::

::: {.column width="50%"}
This is a column on the right.
:::
:::::

# Thank You

```{=html}
<!-- Uncomment if you have a bibliography
## References
-->
```
