---
title: "AAGI"
author: "Analytics for the Australian Grains Industry"
date: last-modified
format:
  aagi-revealjs: default
---

```{r}
#| label: load
#| message: false

if (!require("pak")) install.packages("pak")

if (!require("AAGIPalettes")) {
  pak::pkg_install("AAGI-AUS/AAGIPalettes")
}

if (!require("AAGIThemes")) {
  pak::pkg_install("AAGI-AUS/AAGIThemes")
}

if (!require("gapminder")) {
  pak::pkg_install("gapminder")
}

library(ggplot2)
library(AAGIThemes)

# set ggplot2 theme
theme_set(theme_aagi())
```

## An AAGI Reveal.js Theme for Quarto

This Quarto extension allows you to create your slides using a theme that follows AAGI typography and colour styles and provides the official AAGI logo and cover image for the title slide.

## Basic Tables

[AAGIQuarto](https://github.com/AAGI-AUS/AAGIQuarto) provides basic theming of HTML tables through CSS, for example, this is a markdown table.

```
| Syntax      | Description |
| ----------- | ----------- |
| Header      | Title       |
| Paragraph   | Text        |
```

That renders like this.

| Syntax      | Description |
| ----------- | ----------- |
| Header      | Title       |
| Paragraph   | Text        |

## Advanced Tables

For more advanced tables, we suggest paring with the R package [{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) to provide AAGI themed tables using `theme_gt_aagi()`, that offers more flexibility in formatting.

```{r}
#| label: AAGI table
#| message: false
#| echo: true

library(dplyr)
library(gt)
library(AAGIThemes)

gt <- gt(head(airquality) |>
 mutate(`Month Name` = "May"))
gt <- theme_gt_aagi(gt)
gt
```


## Basic Figures

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming basic figures in R, for example.

```{r}
#| label: graphics-figure
#| message: false
library(AAGIThemes)
plot_aagi(pressure)
```


## Figures with {ggplot2}

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming [{ggplot2}](https://ggplot2.tidyverse.org) outputs in R, for example.

```{r}
#| label: ggplot2-figure
#| message: false
#Prepare data

library(gapminder)
library(dplyr)
library(ggplot2)
library(AAGIThemes)

facet <- gapminder |>
  filter(continent != "Americas") |>
  group_by(continent, year) |>
  summarise(pop = sum(as.numeric(pop)))
#> `summarise()` has grouped output by 'continent'. You can override using the
#> `.groups` argument.

col_values <- c(
  AAGIPalettes::colour_as_hex("AAGI Teal"),
  AAGIPalettes::colour_as_hex("AAGI Green"),
  AAGIPalettes::colour_as_hex("AAGI Yellow"),
  AAGIPalettes::colour_as_hex("AAGI Blue")
)

#Make plot
ggplot() +
  geom_area(data = facet, aes(x = year, y = pop, fill = continent)) +
  scale_fill_manual(values = col_values) +
  facet_wrap(~ continent, ncol = 5) +
  scale_y_continuous(breaks = c(0, 2000000000, 4000000000),
                    labels = c(0, "2bn", "4bn")) +
  theme_aagi() +
  geom_hline(yintercept = 0,
            linewidth = 1,
            colour = "#474747") +
  theme(legend.position = "none", axis.text.x = element_blank()) +
  labs(title = "Asia's rapid growth", subtitle = "Population growth by continent, 1952-2007")
```

## Slides With Columns

:::: {.columns}
::: {.column width="50%"}
This is a column on the left.
:::

::: {.column width="50%"}
This is a column on the right.

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text


to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text

to
much 
text
:::
::::

## More Information

You can learn more about controlling the appearance of RevealJS output here: <https://quarto.org/docs/presentations/revealjs/>

<!-- This background won't show properly in the example rendered slide, but when used with `quarto use template AAGI-AUS/AAGIQuarto`
you will have the closing slide display the same image as the title slide under "Thank You" (or the H1 text of your choosing)
-->
# Thank You{background-image="_extensions/AAGI-AUS/aagi/title-slide-main.png" background-size="1050px auto" background-position="50% 85%"}

<!-- Uncomment if you have a bibliography
## References 
-->