---
# =============================================================================
# AAGI Full PDF Report Template
# =============================================================================
# USAGE (standalone — no _quarto.yml project required)
#
#   1. Install the extension once:
#        quarto add AAGI-AUS/AAGIQuarto
#
#   2. Edit the params block below to match your project.
#
#   3. Render:
#        quarto render template.qmd
#        # or supply params on the command line:
#        quarto render template.qmd \
#          -P uni:AU \
#          -P aagi_staff:"Jane Smith" \
#          -P project_code:UA2026-001
#
# PARAMS
#   uni           Your AAGI node code. One of: CU, AU, UQ
#   aagi_staff    Your full name (used in "Prepared by")
#   project_code  GRDC/AAGI project code, e.g. "UA2026-001ABC"
#   report_title  Short descriptive title for the report
#   partner       Client/partner name
#   partner_email Client/partner contact email
#   aagi_email    Your AAGI correspondence email
# =============================================================================

format:
  aagi-pdf+report:
    fig-path: figures/

execute:
  echo: false

params:
  uni: "CU"
  aagi_staff: "Your Name"
  project_code: "ABC2026-001ABC"
  report_title: "My Report Title"
  partner: "Partner Organisation"
  partner_email: "partner@email.com.au"
  aagi_email: "your.name@example.edu.au"

date: last-modified
date-format: long
bibliography: references.bib
---

```{r}
#| label: setup
#| include: false
#| message: false

# ---------------------------------------------------------------------------
# Package management
# ---------------------------------------------------------------------------

allow_install <- isTRUE(as.logical(
  Sys.getenv("AAGI_AUTO_INSTALL", unset = interactive())
))

ensure_pkg <- function(pkg, github = NULL) {
  if (requireNamespace(pkg, quietly = TRUE)) {
    return(invisible(TRUE))
  }
  if (!allow_install) {
    return(invisible(FALSE))
  }

  # Bootstrap pak on first use
  if (!requireNamespace("pak", quietly = TRUE)) {
    install.packages(
      "pak",
      repos = sprintf(
        "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
        .Platform$pkgType,
        R.Version()$os,
        R.Version()$arch
      )
    )
  }
  tryCatch(
    pak::pak(github %||% pkg, dependencies = TRUE),
    error = function(e) {
      warning(sprintf("Could not install %s: %s", pkg, e$message))
    }
  )
  invisible(requireNamespace(pkg, quietly = TRUE))
}

for (pkg in c("ggplot2", "flextable", "ragg")) {
  ensure_pkg(pkg)
}
for (pkg in c("AAGIThemes", "AAGIPalettes")) {
  ensure_pkg(pkg, github = sprintf("AAGI-AUS/%s", pkg))
}

# ---------------------------------------------------------------------------
# University metadata (resolved from params$uni)
# ---------------------------------------------------------------------------

uni_info <- list(
  CU = list(
    name = "Curtin University",
    node = "CU",
    leads = "Prof Mark Gibberd, Assoc Prof Julia Easton, Prof Adam Sparks"
  ),
  AU = list(
    name = "Adelaide University",
    node = "AU",
    leads = "Assoc Prof Julian Taylor, Dr Olena Kravchuk"
  ),
  UQ = list(
    name = "University of Queensland",
    node = "UQ",
    leads = "Prof Scott Chapman, Emeritus Prof Kaye Basford"
  )
)

# Validate uni param and fall back to CU with a warning
uni_code <- toupper(trimws(params$uni))
if (!uni_code %in% names(uni_info)) {
  warning(
    sprintf(
      "Unknown uni code '%s'. Valid values: %s. Falling back to 'CU'.",
      params$uni,
      toString(names(uni_info))
    ),
    call. = FALSE
  )
  uni_code <- "CU"
}

info <- uni_info[[uni_code]]
uni_name <- info$name
uni_node <- info$node
uni_leads <- info$leads

# ---------------------------------------------------------------------------
# Graphics device (pdf for LaTeX output, png otherwise)
# ---------------------------------------------------------------------------

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = "pdf")
} else {
  knitr::opts_chunk$set(dev = "ragg_png", dpi = 192)
}

knitr::opts_chunk$set(fig.pos = "H", fig.retina = 2)

# ---------------------------------------------------------------------------
# Load and configure AAGI packages
# ---------------------------------------------------------------------------

suppressPackageStartupMessages({
  library(ggplot2)
  if (requireNamespace("AAGIThemes", quietly = TRUE)) {
    library(AAGIThemes)
  }
  if (requireNamespace("AAGIPalettes", quietly = TRUE)) {
    library(AAGIPalettes)
  }
  if (requireNamespace("flextable", quietly = TRUE)) library(flextable)
})

if (exists("theme_aagi")) {
  ggplot2::theme_set(theme_aagi())
}

if (requireNamespace("flextable", quietly = TRUE) && exists("theme_ft_aagi")) {
  flextable::set_flextable_defaults(theme_fun = theme_ft_aagi)
}
```

---
title:    "`r sprintf('Analytics for the Australian Grains Industry - %s (AAGI-%s)\\\nTechnical Report Series: 123', uni_name, uni_node)`"
subtitle: "`r sprintf('%s\\\nReport for %s', params$report_title, params$project_code)`"
author:
  - "`r sprintf('Prepared for: %s (%s)', params$partner, params$partner_email)`"
  - "`r sprintf('Prepared by: %s (%s, AAGI-%s)', params$aagi_staff, uni_name, uni_node)`"
  - "`r sprintf('Project Lead: %s', uni_leads)`"
university: "`r uni_name`"
email:      "`r params$aagi_email`"
---

\newpage

```{=latex}
\clearpage
\setcounter{page}{1}
```

\tableofcontents

\newpage

# Executive Summary

Summarise the work provided by AAGI and the main results. Aim to keep this to
a single page.

\newpage

# Introduction

- Goals of the research project.
- Background, context and rationale behind the research.

## This is a subsection

Use subsections (and subsubsections) as needed to structure your content.

# Experimental/Trial Design

- Trial design type and layout.
- Treatments, number of replicates, blocking.
- Notes on specific considerations (e.g. small plots, glasshouse, breeding
  trials, OFE, bioinformatics).

# Exploratory Data Analysis and Data Visualisation

- Interpretation of data and visualisations.
- Rationale for the statistical methodologies used.

# Methods

- Detailed description of the procedures and methodologies used.
- Software versions, pipeline commits, and input/output details.

# Results and Discussion

Findings and their implications with respect to the research question.

# Figure Example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2} with the AAGI theme."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table Example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable} with the AAGI theme."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

# Datasets and Metadata (Optional)

- Links and DOIs to associated datasets (e.g. GRDC Data Catalogue entries).
- md5/sha256 checksums for input data and outputs.
- Git commit numbers and tags for associated code repositories.

# Trial Location Maps (Optional)

Include if relevant to the project.

# References

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information. Add as many appendix sections as required.
