---
# =============================================================================
# AAGI PDF Report Template
# =============================================================================
# USAGE
#
#   1. Install the extension once:
#        quarto add AAGI-AUS/AAGIQuarto
#
#   2. Edit the params block below to match your project.
#
#   3. Render:
#        quarto render template.qmd
#        # or supply params on the command line:
#        quarto render template.qmd \
#          -P uni:AU \
#          -P aagi_staff:"Jane Smith" \
#          -P project_code:UA2026-001
#
# PARAMS
#   uni                 Your AAGI node code. One of: CU, AU, UQ
#   aagi_staff          Your full name (used in "Prepared by")
#   project_code        GRDC/AAGI project code, e.g. "UA2026-001ABC"
#   report_title        Short descriptive title for the report
#   partner             Client/partner name
#   partner_email       Client/partner contact email
#   aagi_email          Your AAGI correspondence email
# =============================================================================

format:
  aagi-pdf+report:
    fig-path: figures/pdf-report/
    fig-pos: "H"

knitr:
  opts_chunk:
    fig.width:  6.3
    fig.height: 4
    out.width:  "\\linewidth"
    fig.align:  "center"

execute:
  echo: false

params:
  uni:           "CU"
  aagi_staff:    "Your Name"
  project_code:  "ABC2026-001ABC"
  report_title:  "My Report Title"
  partner:       "Partner Organisation"
  partner_email: "partner@email.com.au"
  aagi_email:    "your.name@example.edu.au"

# this makes this a long report; set to false for a short report
has-title-page: true

date:        last-modified
date-format: long
bibliography: references.bib

# title is used in the running page header — keep it short
title: "AAGI Program Report"

# These three fields render as right-aligned teal lines on the title page
programme-line1: "Analytics for the Australian Grains Industry"
programme-line2: "`r sprintf('%s (AAGI-%s)', params$uni_info[[params$uni]]$name, params$uni)`"
programme-line3: "AAGI Program Report"

subtitle:             "`r params$report_title`"
project-code:         "`r params$project_code`"
prepared-for:         "`r params$partner`"
prepared-for-email:   "`r params$partner_email`"
prepared-by:          "`r params$aagi_staff`"
university:           "`r params$uni_info[[params$uni]]$name`"
correspondence-email: "`r params$aagi_email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)

# Set flextable font to system sans-serif — prevents Proxima Nova errors
# on systems where it is not installed. theme_ft_aagi() inherits this.
flextable::set_flextable_defaults(
  theme_fun = AAGIThemes::theme_ft_aagi,
  font.family = if (
    nzchar(Sys.which("fc-list")) &&
      nzchar(system("fc-list 'Proxima Nova'", intern = TRUE)[1])
  ) {
    "Proxima Nova"
  } else if (
    nzchar(Sys.which("fc-list")) &&
      nzchar(system("fc-list 'Arial'", intern = TRUE)[1])
  ) {
    "Arial"
  } else {
    "sans"
  }
)

try(ggplot2::theme_set(AAGIThemes::theme_aagi()), silent = TRUE)
```

# Executive Summary

Summarise the work provided by AAGI and the main results. Aim to keep this to
a single page.

# Introduction

- Goals of the research project.
- Background, context and rationale behind the research.

## This is a subsection

Use subsections (and subsubsections) as needed to structure your content.

# Experimental / Trial Design

- Trial design type and layout.
- Treatments, number of replicates, blocking.
- Notes on specific considerations (e.g. small plots, glasshouse, breeding
  trials, OFE, bioinformatics).

# Exploratory Data Analysis

- Interpretation of data and visualisations.
- Rationale for the statistical methodologies used.

# Methods

- Detailed description of the procedures and methodologies used.
- Software versions, pipeline commits, and input/output details.

# Results and Discussion

Findings and their implications with respect to the research question.
Include citations [@Box1976].

# Figure Example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2} with the AAGI theme."

library(ggplot2)

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table Example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable} with the AAGI theme."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

# References

::: {#refs}
:::

# Metadata and Datasets *(optional)*

- Links and DOIs to associated datasets (*e.g.*, GRDC Data Catalogue entries).
- md5/sha256 checksums for input data and outputs.
- Git commit numbers and tags for associated code repositories.

# Trial Location Maps *(optional)*

Include if relevant to the project.

# Appendix *(optional)*

Additional supporting information. Add as many appendix sections as required.
