---
# Keep exactly one active format per template file.
format:
  # aagi-revealjs: default
  # aagi-pptx: default
  # Report template (active default)
  aagi-pdf+report:
    default: true
    fig-path: figures/pdf-report/
execute:
  echo: false
params:
  # All params can be changed here or at render time, e.g.:
  # quarto render template.qmd -P uni:CU -P pri_bio:Your.Name
  uni: CU
  pri_bio: Your.Name
  project_num: AAA--BBB
  partner: collab_partner
  partner_email: collab_partner@email.com.au
date: last-modified
date-format: long
bibliography: references.bib

title: "Analytics for the Australian Grains Industry - `r if (params$uni == 'CU') 'Curtin University' else if (params$uni == 'AU') 'Adelaide University' else 'University of Queensland'` (AAGI-`r params$uni`)  \n Technical Report Series: 123"
# To force line spacing put two spaces before \n instead of one
subtitle: "Descriptive title for report  \n Report for `r params$project_num`"
author:
  - "Prepared for: `r params$partner` (`r params$partner_email`)"
  - "Prepared by: `r params$pri_bio`, Author 2"
  - "Project Lead: `r if (params$uni == 'CU') 'Curtin University -- Prof Mark Gibberd, Assoc Prof Julia Easton, Prof Adam Sparks' else if (params$uni == 'AU') 'Adelaide University -- Assoc Prof Julian Taylor, Dr Olena Kravchuck' else 'University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford'`"
email: "`r if (params$uni == 'CU') 'cbada@curtin.edu.au' else if (params$uni == 'AU') paste0(params$pri_bio, '@adelaide.edu.au') else paste0(params$pri_bio, '@uq.edu.au')`"
---

```{r}
#| include: false
#| label: variable-based-on-param

if (params$uni == "CU") {
  project_lead <- "Curtin University -- Prof Mark Gibberd, Assoc Prof Julia Easton, Prof Adam Sparks"
  email <- "cbada@curtin.edu.au"
  university <- "Curtin University"
} else if (params$uni == "AU") {
  project_lead <- "Adelaide University -- Assoc Prof Julian Taylor, Dr Olena Kravchuck"
  email <- paste0(params$pri_bio, "@adelaide.edu.au")
  university <- "Adelaide University"
} else {
  project_lead <- "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
  email <- paste0(params$pri_bio, "@uq.edu.au")
  university <- "University of Queensland"
}
```

```{r}
#| label: check-required-packages
#| include: false

required_pkgs <- c("flextable", "ggplot2", "AAGIThemes", "AAGIPalettes")
missing_pkgs <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_pkgs) > 0L) {
  stop(
    "Missing required packages:",
    toString(missing_pkgs),
    "\\nInstall them before rendering, e.g.:",
    "install.packages(c('flextable', 'ggplot2'))",
    "\\ninstall.packages(c('AAGIThemes', 'AAGIPalettes'), repos = c('https://aagi-aus.r-universe.dev', 'https://cloud.r-project.org'))",
    call. = FALSE
  )
}
```

```{r}
#| label: set-the-default-layout
#| include: false

library(flextable)
library(ggplot2)
library(AAGIThemes)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)
```

# To compile a presentation, please see:

-   Revealjs: <https://quarto.org/docs/presentations/revealjs/>

-   PowerPoint: <https://quarto.org/docs/presentations/powerpoint.html>

# Executive summary

What was provided by AAGI and the main results?

-   Citation example (@sparks2018nasapower), another example @butler2017asreml and @brien2020asremlplus.

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# Conclusion or Discussion

-   Summary of the main findings.
-   Implications for the industry (for example).

# Acknowledgements

-   Funding sources.
-   Collaborators.

# References

Cited works and literature.

# Appendix (Optional)

Additional supporting information.
