---
format: 
  # Delete the format that you don't want
  # Presentation
  aagi-revealjs: default
  aagi-pptx: default
  # Report
  aagi-pdf+report: default # full length pdf report
  aagi-pdf+short+report: default # short pdf report (typically one page)
  aagi-docx+report: default # full length word docx report
  aagi-docx+short+report: default # short word docx report (typicall one page)
execute: 
  echo: false
# Delete these if you're using the template for presentation
knitr:
  opts_chunk: 
    fig.path: figures/
params:
# All the params can be changed to align to your organisation and collaborator.
# These can be changed here or in the terminal using the following command with
# each -P represents a parameter:
#             quarto render ... -P $params$:... -P $params2$:/// 
  uni: CU
  pri_bio: Your.Name
  project_num: AAA--BBB
  partner: collab_partner
  partner_email: collab_partner@email.com.au
date: "`r Sys.Date()`"
date-format: long
bibliography: your_references.bib # Replace with your .bib file
---

```{r}
#| include: false
#| label: variable-based-on-param

if (params$uni == "CU") {
  project_lead = "Curtin University -- Prof Mark Gibberd, Dr Julia Easton, Prof Adam Sparks"
  email = "cbada@curtin.edu.au"
  university <- "Curtin University"
} else if (params$uni == "UA") {
  project_lead = "University of Adelaide -- Dr Julian Taylor, Dr Olena Kravchuck"
  email = paste(params$pri_bio, "@adelaide.edu.au", sep = "")
  university <- "University of Adelaide"
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
  email = paste(params$pri_bio, "@uq.edu.au")
  university <- "University of Queensland"
}

```

---
title: "Analytics for the Australian Grains Industry - `r university` (AAGI-`r params$uni`)  \n Technical Report Series: 123"
subtitle: "Descriptive title for report  \n Report for `r params$project_num`"
author:
  - "Prepared for: `r params$partner` (`r params$partner_email`)"
  - "Prepared by: `r params$pri_bio`, Author 2"
  - "Project Lead: `r project_lead`"
email: "`r email`"
---

```{r}
#| label: install-load-aagi-theme
#| include: false

# Install the {pak} package to install AAGI package
if(!requireNamespace("pak", quietly = TRUE)){
  install.packages("pak")
}

# {flextable} is only for word docx output
if(!require(flextable)){
  install.packages("flextable")
}

if(!require(AAGIThemes)){
  pak::pkg_install(
    "AAGI-AUS/AAGIThemes",
    dependencies = TRUE, upgrade = FALSE
  )
}

if(!require(AAGIPalettes)){
  pak::pkg_install(
    "AAGI-AUS/AAGIPalettes",
    dependencies = TRUE, upgrade = FALSE
  )
}

```

```{r}
#| label: set-the-default-layout
#| include: false

library(flextable)
library(ggplot2)
library(AAGIThemes)
library(AAGIPalettes)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)

```

# To compile a presentation, please see:

-   Revealjs: <https://quarto.org/docs/presentations/revealjs/>

-   PowerPoint: <https://quarto.org/docs/presentations/powerpoint.html>

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References

Cited works and literature.

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
