---
format:
  aagi-pdf+report:
    fig-path: figures/pdf-report/

execute:
  echo: false

# ---- Report parameters -------------------------------------------------------
# Adjust these to match your project. The inline R expressions below populate
# the title, subtitle, and author fields automatically from these params.
params:
  uni: "CU" # University key — must match uni_info in setup_reports.R
  aagi_staff: "Your Name"
  project_code: "ABC2026-001"
  report_title: "My Report Title"
  partner: "Collaborating Organisation"
  partner_email: "partner@example.edu.au"
  aagi_email: "your.email@example.edu.au"

date: last-modified
date-format: long
bibliography: references.bib

# Set to true to render a full cover/title page; false for an inline header.
has-title-page: true

title: >
  `r sprintf(
    "Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series",
    params$uni_info[[params$uni]]$name,
    params$uni
  )`

subtitle: >
  `r sprintf("%s — %s", params$report_title, params$project_code)`

author:
  - '`r sprintf("Prepared for: %s (%s)", params$partner, params$partner_email)`'
  - '`r sprintf("Prepared by: %s", params$aagi_staff)`'

university: "`r params$uni_info[[params$uni]]$name`"
correspondence-email: "`r params$aagi_email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

# Executive Summary

What was provided by AAGI and what were the main results?

# Introduction

- Goals of the research project.
- Background, context and rationale.

# Experimental / Trial Design

- Trial design type and layout.
- Treatments, number of replicates.

# Exploratory Data Analysis

- Interpretation of plots and data.
- Example citation: [@Box1976].

# Methods

Detailed description of the procedures used.

# Results and Discussion

Findings and their implications.

# Figure Example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

library(ggplot2)

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table Example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

# References

::: {#refs}
:::

# Metadata and Datasets *(optional)*

- md5sums for input data and outputs.
- Git commit hashes and tags.

# Appendix *(optional)*

Additional supporting information.
