---
format:
  aagi-pdf+short+report:
    fig-path: figures/pdf-short-report/

params:
  report_title: "Example Short Report"

execute:
  echo: false

date: last-modified
date-format: long
bibliography: references.bib
---

```{r}
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

# Section

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc using the various AAGI palette colours. Use \textcolor{aagiteal}{AAGI Teal}, or \textcolor{aagibrightgreen}{AAGI Bright Green}. @tbl-aagipalette shows the standard palette colours available for use.

::: {#tbl-aagipalette}
\centering
\begin{tabular}{|c | c | c | c |}
\hline
\cellcolor{aagibrightgreen}\texttt{aagibrightgreen} &
\cellcolor{aagiteal}\color{white}\texttt{aagiteal} &
\cellcolor{aagiblue}\texttt{aagiblue} &
\cellcolor{aagigreen}\texttt{aagigreen} \\
\hline
\cellcolor{aagiyellow}\texttt{aagiyellow} &
\cellcolor{aagiorange}\texttt{aagiorange} &
\cellcolor{aagiblack}\color{white}\texttt{aagiblack} &
\cellcolor{aagigrey}\texttt{aagigrey} \\
\hline
\end{tabular}

The AAGI palette colours.
:::

## This is a subsection heading

This is an example of a reference [@blah].

\begin{note}
{\bf\color{aagiteal!75!black} Example Note}\quad
Use \verb|\begin{note}...\end{note}| to create coloured notes like this.
\end{note}

Example R code using {AAGIThemes}.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3

plot_aagi(pressure)
```

# Table example using {flextable}

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

### This is a subsubsection heading

\lipsum[1-3]

# Next Section

Add as many sections as needed [@blah].

