---
format:
  aagi-pdf+report:
    fig-path: figures/pdf-report/

execute:
  echo: false

params:
  aagi_staff: "your_name"
  project_code: "ABC2026-001ABC"
  report_title: "My Report Title"
  partner: "collab_partner_org"
  partner_email: "collab_partner@email.com.au"
  aagi_email: "your.email@example.edu.au"

date: last-modified
date-format: long
bibliography: references.bib

has-title-page: true

title: !expr 'sprintf("Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series: 123", params$uni_info[[params$uni]]$name, params$uni)'

subtitle: !expr 'sprintf("%s Report for %s", params$report_title, params$project_code)'

author:
  - !expr 'sprintf("Prepared for: %s (%s)", params$partner, params$partner_email)'
  - !expr 'sprintf("Prepared by: %s", params$aagi_staff)'

university: !expr params$uni_info[[params$uni]]$name
correspondence-email: !expr params$aagi_email
---

```{r}
#| label: setup
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

# Executive summary

What was provided by AAGI and the main results?

# Introduction

- Goals of the research project.
- Background, context and rationale behind the research.

# Experimental/Trial Design

- Trial design type and layout.
- Treatments, number of replicates.

# Exploratory Data Analysis and Data Visualisation

- Interpretation of plots and data.
- Citation [@Box1976]. 

# Methods

- Detailed description of the procedures used.

# Results and Discussion

Findings and their implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

library(ggplot2)

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

# Metadata and Datasets (Optional)

- md5sums for input data and outputs.
- Git commit numbers and tags.

# Appendix (Optional)

Additional supporting information.
