---
format:
  aagi-pdfreport: default
output-file: template-pdf-report.pdf
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  aagi_staff: "your_name"
  project_code: "ABC2026-001ABC"
  report_title: "My Report Title"
  partner: "collab_partner_org"
  partner_email: "partner@example.edu.au"
  aagi_email: "your.email@example.edu.au"   # REQUIRED unless AAGI_EMAIL env var provided
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/aagi/assets/biometrics.csl
title: "Analytics for the Australian Grains Industry — Technical Report"
subtitle: "Report for the project"
author:
  - "Prepared for: collab_partner_org (partner@example.edu.au)"
  - "Prepared by: your_name"
---

```{r}
#| include: false
#| label: setup
# Source centralized setup which exports `uni_name` and `aagi_email`
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block.qmd"}
```

\newpage

```{=latex}
\clearpage
\setcounter{page}{1}
```

\tableofcontents

\newpage

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References

Cited works and literature. @Box1976

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
