---
format:
  AAGI-AUS/aagi-docx+short-report:
    default: true
    fig-path: figures/docx-short-report/

params:
  report_title: "My Report Title"
  project_code: "ABC2026-001ABC"
  aagi_staff: "your_name"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"

date: last-modified
date-format: long
bibliography: references.bib

title: "`r sprintf('Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series: 123', params$uni_info[[params$uni]]$name, params$uni)`"
subtitle: "`r sprintf('%s  \nReport for %s', params$report_title, params$project_code)`"
author:
  - "`r sprintf('Prepared for: %s (%s)', params$partner, params$partner_email)`"
  - "`r sprintf('Prepared by: %s', params$aagi_staff)`"
university: "`r params$uni_info[[params$uni]]$name`"
email: "`r params$uni_info[[params$uni]]$email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

```{r child="_includes/title_block.qmd"}
```

{{< pagebreak >}}

# Executive summary

Concise summary of the work provided by AAGI and the primary findings.

# Introduction

- Goals of the research project.
- Background, context and rationale.

# Experimental / Trial Design

- Trial design and layout.
- Treatments, replicates, blocking, randomisation.

# Exploratory Data Analysis & Visualisation

- Interpretation of key plots.

# Methods

- Detailed procedures, software versions, pipeline commits.

# Analysis

- Statistical approaches and workflow.

# Results and Discussion

- Main findings and implications.

# References

::: {#refs}
:::
