---
title: !expr paste('Progress report for project', params[["project-number"]])
subtitle: "Subtitle here"
category: !expr params[["project-number"]]
params:
  uni: CU
  pri_bio: Your.Name
  project-number: ABC1234-567XYZ
  partner: collab_partner
  partner_email: collab_partner@email.com.au
format: aagi-docx+short+report
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

author: 
  - !expr sprintf("Prepared for: %s (%s)", params[["partner"]], params[["partner_email"]])
  - !expr sprintf("Prepared by: %s, Author 2", params[["pri_bio"]])
  - !expr paste("Project Lead:", 
        if (params[["uni"]] == "CU") "Curtin University -- Prof Mark Gibberd, Assoc Prof Julia Easton, Prof Adam Sparks"
        else if (params[["uni"]] == "UA") "University of Adelaide -- Assoc Prof Julian Taylor, Dr Olena Kravchuck"
        else "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
      )
  - !expr paste(
        "email:", 
        if (params[["uni"]] == "CU") "cbada@curtin.edu.au"
        else if (params[["uni"]] == "UA") paste0(params[["pri_bio"]], "@adelaide.edu.au")
        else paste0(params[["pri_bio"]], "@uq.edu.au")
    )
subject: !expr (
  if (params[["uni"]] == "CU") "cbada@curtin.edu.au"
  else if (params[["uni"]] == "UA") paste0(params[["pri_bio"]], "@adelaide.edu.au")
  else paste0(params[["pri_bio"]], "@uq.edu.au")
)
---

```{r}
#| include: false
#| label: setup

if (
  toupper(Sys.info()["sysname"]) == "LINUX" ||
    toupper(Sys.info()["sysname"]) == "DARWIN"
) {
  knitr::opts_chunk$set(dev = "cairo_pdf")
}

if (require(xtable)) {
  options(xtable.comment = FALSE)
}
if (require(formatR)) {
  options(formatR.arrow = FALSE)
  knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 60)
  )
}

if (!require(pak)) {
  install.packages(
    "pak",
    repos = sprintf(
      "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
      .Platform$pkgType,
      R.Version()$os,
      R.Version()$arch
    )
  )
}
if (!require(flextable)) {
  pak::pak("flextable", dependencies = TRUE)
}

# Integrating with AAGIPalettes, AAGIThemes
if (!require(AAGIThemes)) {
  pak::pak("AAGI-AUS/AAGIThemes", dependencies = TRUE)
}
if (!require(AAGIPalettes)) {
  pak::pak("AAGI-AUS/AAGIPalettes", dependencies = TRUE)
}

library(AAGIThemes)
library(AAGIPalettes)
library(flextable)
library(ggplot2)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(theme_fun = theme_ft_aagi)
```

```{r}
#| include: false
#| label: config-for-title

if (params$uni == "CU") {
  project_lead = "Curtin University -- Prof Mark Gibberd, Assoc Prof Julia Easton, Prof Adam Sparks"
  email = "cbada@curtin.edu.au"
} else if (params$uni == "UA") {
  project_lead = "University of Adelaide -- Assoc Prof Julian Taylor, Dr Olena Kravchuck"
  email = paste(params$pri_bio, "adelaide.edu.au", sep = "")
} else {
  project_lead = "University of Queensland -- Prof Scott Chapman, Emeritus Prof Kaye Basford"
  email = paste(params$pri_bio, "@uq.edu.au", sep = "")
}
```

# Section 1

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

```{r}
#| label: tbl-example
#| tbl-cap: "Here is a table."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

### This is a subsubsection heading

And so on.

# Next Section

Add as many sections as needed.

# References
