---
format:
  aagi-htmlreport:
    toc: true
    self-contained: true
output-file: template-html-report.html
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  aagi_staff: "your_name"
  project_code: "ABC2026-001ABC"
  report_title: "My Report Title"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"
  aagi_email: "your.email@example.edu.au"    # REQUIRED unless AAGI_EMAIL env var provided
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/aagi/assets/biometrics.csl

# Minimal static metadata only (no inline R)
title: "Analytics for the Australian Grains Industry — Technical Report"
subtitle: "Report for the project"
author:
  - "Prepared for: collab_partner_org (partner@example.com)"
  - "Prepared by: your_name"
---

```{r}
#| label: setup
#| include: false
#| message: false
# Source centralized setup (must run before inline R in title block and before plots)
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block.qmd"}
```

# Executive Summary

This document demonstrates the **AAGI HTML report format** provided by the `AAGIQuarto` extension.
It renders a fully styled, self-contained HTML report using AAGI branding — AAGI teal headings, teal table headers with alternating row shading, teal hyperlinks, and an AAGI-styled note callout.

Use this format for sharing AAGI technical reports as web-ready HTML documents.

# Introduction

The `aagi-html-report` format applies AAGI branding to Quarto HTML output:

- Teal headings and hyperlinks matching the AAGI colour palette.
- Table styling with a teal header row, white text, and alternating row backgrounds.
- A note callout styled to match the LaTeX `tcolorbox` note environment.
- Table of contents and numbered sections for longer reports.
- A title block styled with AAGI colours.

To use this format in your own document:

```{.yaml filename="AAGI_HTML_report"}
#| eval: FALSE
format:
  aagi-htmlreport: default
```

Then render with:

```{bash}
#| eval: FALSE
quarto render your-report.qmd --to aagi-htmlreport
```

# Experimental/Trial Design

- Trial design type and layout.
- Treatments, number of replicates.
- Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

- Interpretation of plots and data.
- Rationale behind specific methods used.

# Methods

Detailed description of the procedures and methodologies used.

# Results and Discussion

Findings and their implications.

## Note callout example

Use Quarto's built-in callout note for important information:

::: {.callout-note}
This is an AAGI-styled note callout, analogous to the `note` environment in the LaTeX PDF report template. Use it to highlight important information for the reader.
:::

Alternatively, use the `.aagi-note` class for the tcolorbox-style appearance:

::: {.aagi-note}
This is an `.aagi-note` div. It mimics the left- and right-bordered teal box from the LaTeX template.
:::

## Table example

AAGI table styling is applied automatically to all Markdown tables. The header row uses AAGI teal with white text, and rows alternate between AAGI grey and white.

| Treatment | Replicate | Yield (t/ha) | Protein (%) |
|-----------|-----------|:------------:|:-----------:|
| Control   | 1         | 3.21         | 11.4        |
| Control   | 2         | 3.08         | 11.8        |
| Nitrogen  | 1         | 4.15         | 12.9        |
| Nitrogen  | 2         | 4.32         | 13.1        |

: Trial results summary {#tbl-results}

## Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2} with the AAGI theme."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point(colour = "#00808b") +
  theme_aagi()
```

# Metadata and Datasets (Optional)

- md5sums for input data and outputs (if applicable).
- Git commit numbers and tags.
- Location of outputs (FAIR Data).
- DOI for AAGI outputs.

# References

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
