---
title: !expr paste('Progress report for project', params[["project-number"]])
subtitle: "Subtitle here"
category: !expr params[["project-number"]]
params:
  uni:
    values: [CU, AU, UQ]
  pri_bio: Your.Name
  project-number: ABC1234-567XYZ
  partner: collab_partner
  partner_email: collab_partner@email.com.au
format: aagi-docx+short+report
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl
author:
  - !expr sprintf("Prepared for: %s (%s)", params$partner,
      params$project_code)
  - !expr sprintf("Prepared by: %s", params$pri_bio)
email: !expr if (params$uni == "CU") "cbada@curtin.edu.au" else if (params$uni == "AU") paste0(params$pri_bio, "@adelaide.edu.au") else paste0(params$pri_bio, "@uq.edu.au")
---

```{r}
#| label: setup
#| include: FALSE
#| message: FALSE

if (!requireNamespace("pak", quietly = TRUE)) {
  install.packages(
    "pak",
    repos = sprintf(
      "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
      .Platform$pkgType,
      R.Version()$os,
      R.Version()$arch
    )
  )
}

ensure_pkg <- function(pkg, github = NULL) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    if (!is.null(github)) {
      pak::pak(github, dependencies = TRUE)
    } else {
      pak::pak(pkg, dependencies = TRUE)
    }
  }
}

ensure_pkg("ggplot2")
ensure_pkg("flextable")
ensure_pkg("AAGIThemes", github = "AAGI-AUS/AAGIThemes")
ensure_pkg("AAGIPalettes", github = "AAGI-AUS/AAGIPalettes")

library(ggplot2)
library(flextable)
library(AAGIThemes)
library(AAGIPalettes)
```

# Section 1

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

```{r}
#| label: tbl-example
#| tbl-cap: "Here is a table."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

### This is a subsubsection heading

And so on.

# Next Section

Add as many sections as needed.

# References
