---
format: aagi-pdfshortreport
output-file: template-pdf-short-report.pdf
params:
  report_title: "My Report Title"
  project_code: "ABC2026-001ABC"
  aagi_staff: "your_name"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"
  aagi_email: "contact@example.com"      # required (or set AAGI_EMAIL env var)
  report_number: "123"
  report_version: "1.0"
  authors:
    - "Alice A."
    - "Bob B."
  abstract: "Short abstract (1–2 sentences)."
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/aagi/assets/biometrics.csl
title: "Analytics for the Australian Grains Industry — Technical Report"
subtitle: "Short report for the project"
author:
  - "Prepared for: collab_partner_org (partner@example.com)"
  - "Prepared by: your_name"
---

```{r}
#| label: setup
#| include: false
#| message: false
# Source centralized setup (must run before inline R in title block and before plots)
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block_short.qmd"}
```

# Section 

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc using the various AAGI palette colours. Use `\textcolor{aagiteal}{...}` for `\textcolor{aagiteal}{AAGI Teal}`, or `\textcolor{aagibrightgreen}{...}` for `\textcolor{aagibrightgreen}{AAGI Bright Green}`, for instance. @tbl-aagipalette shows the standard palette colours available for use.

::: {#tbl-aagipalette}
  \centering
  \begin{tabular}{|c | c | c | c |}
    \hline
    \cellcolor{aagibrightgreen}\texttt{aagibrightgreen} & %
    \cellcolor{aagiteal}\color{white}\texttt{aagiteal} & %
    \cellcolor{aagiblue}\texttt{aagiblue} & %
    \cellcolor{aagigreen}\texttt{aagigreen} \\
    \hline
    \cellcolor{aagiyellow}\texttt{aagiyellow} & %
    \cellcolor{aagiorange}\texttt{aagiorange} & %
    \cellcolor{aagiblack}\color{white}\texttt{aagiblack} & %
    \cellcolor{aagigrey}\texttt{aagigrey} \\
    \hline
  \end{tabular} 

The AAGI palette colours.
:::

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

\begin{note}
  {\bf\color{aagiteal!75!black} Example Note}\quad
  Use \verb|\begin{note}...\end{note}| to create coloured notes like this
  that stand out on the page.
\end{note}

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3

plot_aagi(pressure)
```

# Table example using {flextable}

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

### This is a subsubsection heading

\lipsum[1-3]

And so on.

# Next Section

Add as many sections as needed.

# References
