---
format: aagi-docx+report
params:
  # override values that differ from root _quarto.yml; otherwise inherit
  report_title: "My Report Title"
  project_code: "ABC2026-001ABC"
  aagi_staff: "your_name"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"

date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

# Compute title/subtitle/author/university/email from params and params$uni_info
title: "`r sprintf('Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series: 123', params$uni_info[[params$uni]]$name, params$uni)`"
subtitle: "`r sprintf('%s\nReport for %s', params$report_title, params$project_code)`"
author:
  - "`r sprintf('Prepared for: %s (%s)', params$partner, params$partner_email)`"
  - "`r sprintf('Prepared by: %s', params$aagi_staff)`"
university: "`r params$uni_info[[params$uni]]$name`"
email: "`r params$uni_info[[params$uni]]$email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

# Source centralized setup (must run before inline R in child include and before plots)
source("_scripts/setup.R", local = TRUE)
```

```{r child="_includes/title-block.qmd"}
```

{{< pagebreak >}}

# Executive summary

Concise summary of the work provided by AAGI and the primary findings.

# Introduction

- Goals of the research project.
- Background, context and rationale.

# Experimental / Trial Design

- Trial design and layout.
- Treatments, replicates, blocking, randomisation.
- Special considerations (small plots, glasshouse, genetics, breeding, OFE, bioinformatics).

# Exploratory Data Analysis & Visualisation

- Interpretation of key plots.
- Rationale for visualization choices.

# Methods

- Detailed procedures, software versions, pipeline commits.
- Input/output descriptions and pre-processing steps.

# Analysis

- Statistical approaches and workflow.
- Model specifications and diagnostics.

# Results and Discussion

- Main findings and implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

library(ggplot2)
ggplot(pressure, aes(temperature, pressure)) +
  geom_point() +
  theme_aagi()
```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)
ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
ft
```

# Metadata & Datasets (Optional)

- md5sums or checksums for inputs/outputs.
- Git commit hashes and tags.
- Output locations (FAIR Data) and DOIs.

# Map (Optional)

Include maps or geospatial outputs if relevant.

# References

::: {#refs}
:::

# Appendix (Optional)

Supplementary information, extended tables, code snippets.
