---
format:
  aagi-htmlshortreport:
    toc: true
    self-contained: true
output-file: template-html-short-report.html
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  aagi_staff: "your_name"
  project_code: "ABC2026-001ABC"
  report_title: "My Short Report"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"
  aagi_email: "your.email@example.edu.au"  # REQUIRED unless AAGI_EMAIL env var provided
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/aagi/assets/biometrics.csl

title: "Analytics for the Australian Grains Industry — Short Report"
subtitle: "Short report for the project"
author:
  - "Prepared for: collab_partner_org (partner@example.com)"
  - "Prepared by: your_name"
---

```{r}
#| label: setup
#| include: false
#| message: false
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block_short.qmd"}
```

# Executive Summary {#executive-summary}

Executive summary goes here.
Summarise the work provided by AAGI and the main results.

# Key findings

-   Finding 1
-   Finding 2
-   Finding 3

::: {.aagi-note}
**NOTE** — This is an example of an AAGI note callout.
:::

# Methods (brief)

Briefly describe the analysis approach and any key assumptions.

# Results (brief)

Summarise the primary results, with 1–2 key figures/tables as needed.

# References

::: {#refs}
:::
