---
format:
  aagi-html+report:
    toc: true
    self-contained: true
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  aagi_staff: "your_name"
  project_code: "ABC2026-001ABC"
  report_title: "My Report Title"
  partner: "collab_partner_org"
  partner_email: "collab_partner@email.com.au"
  aagi_email: "your.email@example.edu.au"

date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

title: "`r sprintf('Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series: 123', params$uni_info[[params$uni]]$name, params$uni)`"
subtitle: "`r sprintf('%s\nReport for %s', params$report_title, params$project_code)`"
author:
  - "`r sprintf('Prepared for: %s (%s)', params$partner, params$partner_email)`"
  - "`r sprintf('Prepared by: %s', params$aagi_staff)`"
university: "`r params$uni_info[[params$uni]]$name`"
email: "`r params$aagi_email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

# Source centralized setup (must run before inline R in title block and before plots)
source("_scripts/setup_reports.R", local = TRUE)
```

::: {.aagi-titlepage}

![](_extensions/AAGI-AUS/aagi/assets/AAGI_logo.svg){.aagi-logo}

:::: {.aagi-title_block}
**Analytics for the Australian Grains Industry**  
**`r uni_name` (AAGI-`r params$uni`)**  
**AAGI Program Report**

# `r params$report_title`

## Report for `r params$project_code`

Prepared for: **`r params$partner` (`r params$partner_email`)**  
Prepared by: **`r params$aagi_staff`**  
Correspondence email: <`r params$aagi_email`>  
_Last updated: `r Sys.Date()`_
::::

![](_extensions/AAGI-AUS/aagi/assets/AAGI_SP_Logo_Block-Portrait.svg){.aagi-partners}
:::

# Executive Summary

This document demonstrates the **AAGI HTML report format** provided by the `AAGIQuarto` extension.
It renders a fully styled, self-contained HTML report using AAGI branding — AAGI teal headings, teal table headers with alternating row shading, teal hyperlinks, and an AAGI-styled note callout.

Use this format for sharing AAGI technical reports as web-ready HTML documents.

# Introduction

The `aagi-html+report` format applies AAGI branding to Quarto HTML output:

- Teal headings and hyperlinks matching the AAGI colour palette.
- Table styling with a teal header row, white text, and alternating row backgrounds.
- A note callout styled to match the LaTeX `tcolorbox` note environment.
- Table of contents and numbered sections for longer reports.
- A title block styled with AAGI colours.

To use this format in your own document:

```{.yaml filename="AAGI_HTML_report"}
#| eval: FALSE
format:
  aagi-html+report: default
```

Then render with:

```{bash}
#| eval: FALSE
quarto render your-report.qmd --to aagi-html+report
```

# Experimental/Trial Design

- Trial design type and layout.
- Treatments, number of replicates.
- Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

- Interpretation of plots and data.
- Rationale behind specific methods used.

# Methods

Detailed description of the procedures and methodologies used.

# Results and Discussion

Findings and their implications.

## Note callout example

Use Quarto's built-in callout note for important information:

::: {.callout-note}
This is an AAGI-styled note callout, analogous to the `note` environment in the LaTeX PDF report template. Use it to highlight important information for the reader.
:::

Alternatively, use the `.aagi-note` class for the tcolorbox-style appearance:

::: {.aagi-note}
This is an `.aagi-note` div. It mimics the left- and right-bordered teal box from the LaTeX template.
:::

## Table example

AAGI table styling is applied automatically to all Markdown tables. The header row uses AAGI teal with white text, and rows alternate between AAGI grey and white.

| Treatment | Replicate | Yield (t/ha) | Protein (%) |
|-----------|-----------|:------------:|:-----------:|
| Control   | 1         | 3.21         | 11.4        |
| Control   | 2         | 3.08         | 11.8        |
| Nitrogen  | 1         | 4.15         | 12.9        |
| Nitrogen  | 2         | 4.32         | 13.1        |

: Trial results summary {#tbl-results}

## Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2} with the AAGI theme."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point(colour = "#00808b") +
  theme_aagi()
```

# Metadata and Datasets (Optional)

- md5sums for input data and outputs (if applicable).
- Git commit numbers and tags.
- Location of outputs (FAIR Data).
- DOI for AAGI outputs.

# References

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
