---
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  uni:
    values: [CU, AU, UQ]
  pri_bio: Your.Name
  project_num: AAA--BBB
  partner: collab_partner
  partner_email: collab_partner@email.com.au
date: last-modified
date-format: long
format: aagi-pdf+report
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

title: !expr paste(
  "Analytics for the Australian Grains Industry -",
  if (params$uni == "CU") "Curtin University"
    else if (params$uni == "AU") "Adelaide University"
    else "University of Queensland",
  sprintf("(AAGI-%s)\nTechnical Report Series: 123", params$uni)
)
subtitle: !expr paste0("Descriptive title for report  \nReport for ", params$project_num)
author:
  - !expr sprintf("Prepared for: %s (%s)", params$partner, params$partner_email)
  - !expr sprintf("Prepared by: %s, Author 2", params$pri_bio)
email: !expr if (params$uni == "CU") "cbada@curtin.edu.au"
       else if (params$uni == "UA") paste0(params$pri_bio, "@adelaide.edu.au")
       else paste0(params$pri_bio, "@uq.edu.au")
---

```{r}
#| label: setup session for R
#| include: FALSE
#| message: FALSE

# Ensure pak is installed (using custom repo block)
if (!requireNamespace("pak", quietly = TRUE)) {
  install.packages(
    "pak",
    repos = sprintf(
      "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
      .Platform$pkgType,
      R.Version()$os,
      R.Version()$arch
    )
  )
}
ensure_pkg <- function(pkg, github = NULL) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    if (!is.null(github)) {
      pak::pak(github, dependencies = TRUE)
    } else {
      pak::pak(pkg, dependencies = TRUE)
    }
  }
}
# PDF device for Linux/Mac (optional)
if (toupper(Sys.info()[["sysname"]]) %in% c("LINUX", "DARWIN")) {
  knitr::opts_chunk$set(dev = "cairo_pdf")
}
ensure_pkg("ggplot2")
ensure_pkg("flextable")
ensure_pkg("AAGIThemes", github = "AAGI-AUS/AAGIThemes")
ensure_pkg("AAGIPalettes", github = "AAGI-AUS/AAGIPalettes")
library(ggplot2)
library(flextable)
library(AAGIThemes)
library(AAGIPalettes)
theme_set(theme_aagi())
set_flextable_defaults(theme_fun = theme_ft_aagi)
```

\newpage

```{=latex}
\clearpage
\setcounter{page}{1}
```

\tableofcontents

\newpage

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References

Cited works and literature. @Box1976

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
