---
format:
  aagi-docxshortreport: default
output-file: template-docx-short-report.docx
params:
  report_title: "My Report Title"
  project_code: "ABC2026-001ABC"
  aagi_staff: "your_name"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"
  aagi_email: "contact@example.com"      # required (or set AAGI_EMAIL env var)
  report_number: "123"
  report_version: "1.0"
  authors:
    - "Alice A."
    - "Bob B."
  abstract: "Short abstract (1–2 sentences)."
date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/aagi/assets/biometrics.csl
title: "Analytics for the Australian Grains Industry — Technical Report"
subtitle: "Short report for the project"
author:
  - "Prepared for: collab_partner_org (partner@example.com)"
  - "Prepared by: your_name"
---

```{r}
#| include: false
# Source centralized setup which exports `uni_name` and `aagi_email`
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block_short.qmd"}
```

# Executive Summary {#executive-summary}

Executive summary goes here.
Summarise the work provided by AAGI and the main results.

# Key findings

-   Finding 1
-   Finding 2
-   Finding 3

::: {.aagi-note}
**NOTE** — This is an example of an AAGI note callout.
:::

# Methods (brief)

Briefly describe the analysis approach and any key assumptions.

# Results (brief)

Summarise the primary results, with 1–2 key figures/tables as needed.

# References

::: {#refs}
:::
