---
format:
  AAGI-AUS/aagi-pdf+report:
    fig-path: figures/pdf-report/
    fig-pos: "H"

knitr:
  opts_chunk:
    fig.width: 6.3
    fig.height: 4
    out.width: "\\linewidth"
    fig.align: "center"

execute:
  echo: false

params:
  uni: "CU"
  uni_name: "Curtin University"
  aagi_staff: "Your Name"
  project_code: "ABC2026-001"
  report_title: "My Report Title"
  partner: "Collaborating Organisation"
  partner_email: "partner@example.edu.au"
  aagi_email: "your.email@example.edu.au"

date: last-modified
date-format: long
bibliography: references.bib
has-title-page: true

# title is used in the running page header — keep it short
title: "AAGI Program Report"

# These three fields render as right-aligned teal lines on the title page
programme-line1: "Analytics for the Australian Grains Industry"
programme-line2: "Curtin University (AAGI-CU)"
programme-line3: "AAGI Program Report"
subtitle: "My Report Title"
project-code: "ABC2026-001"

prepared-for: "Collaborating Organisation"
prepared-for-email: "partner@example.edu.au"
prepared-by: "Your Name"
university: "Curtin University"
correspondence-email: "your.email@example.edu.au"
---

```{r}
#| label: setup
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

# Executive Summary

What was provided by AAGI and what were the main results?

# Introduction

- Goals of the research project.
- Background, context and rationale.

# Experimental / Trial Design

- Trial design type and layout.
- Treatments, number of replicates.

# Exploratory Data Analysis

- Interpretation of plots and data.
- Example citation: [@Box1976].

# Methods

Detailed description of the procedures used.

# Results and Discussion

Findings and their implications.

# Figure Example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

library(ggplot2)

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table Example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

# References

::: {#refs}
:::

# Metadata and Datasets *(optional)*

- md5sums for input data and outputs.
- Git commit hashes and tags.

# Appendix *(optional)*

Additional supporting information.
