---
format:
  AAGI-AUS/aagi-pdf+shortreport:
    fig-path: figures/pdf-short-report/

execute:
  echo: false

date: last-modified
date-format: long
bibliography: references.bib
toc: true

title:              "Example Short Report"
subtitle:           "Optional subtitle here"
short-title:        "AAGI-XX-XXXX"
prepared-for:       "Client 1, Client 2"
prepared-for-org:   "Organisation"
prepared-by:        "Author 1, Author 2"
university:         "Curtin University"
aagi-node:          "AAGI-CU"
correspondence-email: "your.email@example.edu.au"
---

```{r}
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
# Set flextable font to system sans-serif — prevents Proxima Nova errors
# on systems where it is not installed. theme_ft_aagi() inherits this.
flextable::set_flextable_defaults(
  theme_fun = AAGIThemes::theme_ft_aagi,
  font.family = if (
    nzchar(Sys.which("fc-list")) &&
      nchar(system("fc-list 'Proxima Nova'", intern = TRUE)[1]) > 0
  ) {
    "Proxima Nova"
  } else if (
    nzchar(Sys.which("fc-list")) &&
      nchar(system("fc-list 'Arial'", intern = TRUE)[1]) > 0
  ) {
    "Arial"
  } else {
    "sans"
  }
)
try(ggplot2::theme_set(AAGIThemes::theme_aagi()), silent = TRUE)
```

# Section {#sec-main}

This template is designed for smaller ("one-page") AAGI reports.
The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc. using the various AAGI palette colours.
Use \textcolor{aagiteal}{AAGI Teal}, or \textcolor{aagibrightgreen}{AAGI Bright Green}.
@tbl-aagipalette shows the standard palette colours available for use.

```{r}
#| label: tbl-aagipalette
#| tbl-cap: "The AAGI palette colours."

library(flextable)

palette_df <- data.frame(
  Col1 = c("aagibrightgreen", "aagiyellow"),
  Col2 = c("aagiteal", "aagiorange"),
  Col3 = c("aagiblue", "aagiblack"),
  Col4 = c("aagigreen", "aagigrey")
)

flextable(palette_df) |>
  delete_part("header") |>
  bg(i = 1, j = 1, bg = "#B6D438") |>
  bg(i = 2, j = 1, bg = "#FFBC42") |>
  bg(i = 1, j = 2, bg = "#00808B") |>
  bg(i = 2, j = 2, bg = "#EC8525") |>
  bg(i = 1, j = 3, bg = "#648FD2") |>
  bg(i = 2, j = 3, bg = "#414042") |>
  bg(i = 1, j = 4, bg = "#54921E") |>
  bg(i = 2, j = 4, bg = "#F2F2F2") |>
  color(i = 1, j = 2, color = "white") |>
  color(i = 2, j = 3, color = "white") |>
  border_outer(border = officer::fp_border(color = "white", width = 2)) |>
  border_inner(border = officer::fp_border(color = "white", width = 2)) |>
  autofit() |>
  theme_ft_aagi()
```

## This is a subsection heading

This is an example of a reference [@blah].

\begin{note}
{\sffamily\bfseries\color{aagiteal!75!black} NOTE}
Use \verb|\begin{note}...\end{note}| to create coloured notes like this.
\end{note}

Example R code using {AAGIThemes}.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3

plot_aagi(pressure)
```

As shown in @fig-example1, the pressure relationship is illustrated.

# Table example using {flextable}

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

### This is a subsubsection heading

Add body text here.

# Next Section

Add as many sections as needed [@blah].

# References

::: {#refs}
:::
