---
format: aagi-docxshortreport
output-file: template-docx-short-report.docx
params:
  # override values that differ from root _quarto.yml; everything else inherits
  report_title: "My Report Title"
  project_code: "ABC2026-001ABC"
  aagi_staff: "your_name"
  partner: "collab_partner_org"
  partner_email: "partner@example.com"
  aagi_email: "contact@example.com"
  # optional metadata used by title_block_long.qmd (add only if needed)
  report_number: "123"
  report_version: "1.0"
  authors: ["Alice A.", "Bob B."]
  abstract: "Short abstract (1–2 sentences)."

date: last-modified
date-format: long
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

# Title / subtitle / author / contact derived from params
title: "`r sprintf('Analytics for the Australian Grains Industry - %s (AAGI-%s) Technical Report Series: %s', params$uni_info[[params$uni]]$name, params$uni, params$report_number %||% '')`"
subtitle: "`r sprintf('%s\\nReport for %s', params$report_title, params$project_code)`"
author:
  - "`r sprintf('Prepared for: %s (%s)', params$partner, params$partner_email)`"
  - "`r sprintf('Prepared by: %s', paste(params$authors %||% params$aagi_staff, collapse = ', '))`"
university: "`r params$uni_info[[params$uni]]$name`"
email: "`r params$aagi_email`"
---

```{r}
#| label: setup
#| include: false
#| message: false

# Source centralized setup script. This must exist at _scripts/setup.R (repo root).
# It will export uni_name and set knitr options/device/theme.
source("_scripts/setup_reports.R", local = TRUE)
```

```{r child="_includes/title_block_short.qmd"}
```

# Executive Summary {#executive-summary}

Executive summary goes here.
Summarise the work provided by AAGI and the main results.

# Key findings

-   Finding 1
-   Finding 2
-   Finding 3

::: {.aagi-note}
**NOTE** — This is an example of an AAGI note callout.
:::

# Methods (brief)

Briefly describe the analysis approach and any key assumptions.

# Results (brief)

Summarise the primary results, with 1–2 key figures/tables as needed.

# References

::: {#refs}
:::
