---
execute:
  echo: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
params:
  uni: CU
  pri_bio: Your.Name
  project_num: AAA--BBB
  partner: collab_partner
  partner_email: collab_partner@email.com.au
date: last-modified
date-format: long
format: aagi-pdf+report
bibliography: references.bib
csl: _extensions/AAGI-AUS/aagi/assets/biometrics.csl

title: !expr paste(
  "Analytics for the Australian Grains Industry -",
  if (params$uni == "CU") "Curtin University"
    else if (params$uni == "UA") "University of Adelaide"
    else "University of Queensland",
  sprintf("(AAGI-%s)\nTechnical Report Series: 123", params$uni)
)
subtitle: !expr paste0("Descriptive title for report  \nReport for ", params$project_num)
author:
  - !expr sprintf("Prepared for: %s (%s)", params$partner, params$partner_email)
  - !expr sprintf("Prepared by: %s, Author 2", params$pri_bio)
email: !expr if (params$uni == "CU") "cbada@curtin.edu.au"
       else if (params$uni == "UA") paste0(params$pri_bio, "@adelaide.edu.au")
       else paste0(params$pri_bio, "@uq.edu.au")
---

```{r}
#| label: email for project biometrician
#| include: false

if (params$uni == "CU") {
  email = "cbada@curtin.edu.au"
} else if (params$uni == "UA") {
  email = paste(params$pri_bio, "@adelaide.edu.au", sep = "")
} else {
  email = paste(params$pri_bio, "@uq.edu.au")
}
```

```{r}
#| label: title param
#| include: false

if (params$uni == "CU") {
  university <- "Curtin University"
} else if (params$uni == "UA") {
  university <- "University of Adelaide"
} else {
  university <- "University of Queensland"
}
```

```{r}
#| label: Project number
#| include: false

Pro_Num = params$project_num
```

```{r}
#| label: load
#| message: false

if (!require(pak)) {
  install.packages(
    "pak",
    repos = sprintf(
      "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
      .Platform$pkgType,
      R.Version()$os,
      R.Version()$arch
    )
  )
}
if (!require(flextable)) {
  pak::pak("flextable", dependencies = TRUE)
}

# Integrating with AAGIPalettes, AAGIThemes
if (!require(AAGIThemes)) {
  pak::pak("AAGI-AUS/AAGIThemes", dependencies = TRUE)
}
if (!require(AAGIPalettes)) {
  pak::pak("AAGI-AUS/AAGIPalettes", dependencies = TRUE)
}

library(ggplot2)
library(AAGIThemes)
library(flextable)
library(dplyr)

# set ggplot2 theme
theme_set(theme_aagi())

# set flextable theme
set_flextable_defaults(
  theme_fun = theme_ft_aagi
)
```

\newpage

```{=latex}
\clearpage
\setcounter{page}{1}
```

\tableofcontents

\newpage

# Executive summary

What was provided by AAGI and the main results?

# Introduction

-   Goals of the research project.

-   Background, context and rationale behind the research.

# Experimental/Trial Design

-   Trial design type and layout.

-   Treatments, number of replicates.

-   Specific considerations for small plots, glasshouse, genetics, breeding trials, OFE projects, or bioinformatics.

# Exploratory Data Analysis and Data Visualisation

-   Interpretation of plots and data.

-   Rationale behind specific methods used.

# Methods

-   Detailed description of the procedures and methodologies used.

-   Include versions/commits on developed pipelines, scripts, and input/output details if applicable.

# Analysis (if separate from Methods)

Approach taken for data analysis.

# Results and Discussion

Findings and their implications.

# Figure example

```{r}
#| label: fig-example
#| fig-cap: "An example figure using {ggplot2}."

ggplot(data = pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  theme_aagi()
```

# Table example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

# Metadata and Datasets (Optional)

-   md5sums for input data and outputs (if applicable).

-   Git commit numbers and tags.

-   Location of outputs (FAIR Data).

-   DOI for AAGI outputs.

# Map (Location, Optional)

Include if relevant to the project.

# References

Cited works and literature. @Box1976

::: {#refs}
:::

# Appendix (Optional)

Additional supporting information.
