---
format:
  aagi-pdf+short-report:
    fig-path: figures/pdf-short-report/

execute:
  echo: false

params:
  report_title: "Example Short Report"

date: last-modified
date-format: long
bibliography: references.bib

# Short reports use an inline title block (no separate cover page).
# Fields below populate the header rendered by the template.
title: "`r params$report_title`"
# subtitle, university, correspondence-email are all optional — uncomment if needed:
# subtitle: "Optional subtitle"
# university: "University Name"
# correspondence-email: "your.email@example.edu.au"
---

```{r}
#| include: false
#| message: false

source(file.path("_scripts", "setup_reports.R"), local = TRUE)
```

# Section

This template is designed for shorter ("one-page") AAGI reports. The AAGI logo
appears on the first page only; subsequent pages carry a running title in the
header and the SP logo block in the footer.

Colour names available throughout: `aagiteal`, `aagibrightgreen`, `aagigreen`,
`aagiblue`, `aagiyellow`, `aagiorange`, `aagiblack`, `aagigrey`.

@tbl-aagipalette shows the full palette.

::: {#tbl-aagipalette}
\centering
\begin{tabular}{|c | c | c | c |}
\hline
\cellcolor{aagibrightgreen}\texttt{aagibrightgreen} &
\cellcolor{aagiteal}\color{white}\texttt{aagiteal} &
\cellcolor{aagiblue}\texttt{aagiblue} &
\cellcolor{aagigreen}\texttt{aagigreen} \\
\hline
\cellcolor{aagiyellow}\texttt{aagiyellow} &
\cellcolor{aagiorange}\texttt{aagiorange} &
\cellcolor{aagiblack}\color{white}\texttt{aagiblack} &
\cellcolor{aagigrey}\texttt{aagigrey} \\
\hline
\end{tabular}

The AAGI palette colours.
:::

## Subsection heading

Example citation: [@blah].

\begin{note}
{\bf\color{aagiteal!75!black} Note}\quad
Use \verb|\begin{note}...\end{note}| for highlighted callouts.
\end{note}

# Figure Example

```{r}
#| label: fig-example
#| fig-cap: "An example figure."
#| fig-height: 3

plot_aagi(pressure)
```

# Table Example

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

library(flextable)

flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()
```

# References

::: {#refs}
:::
