---
format: aagi-pptx
execute:
  echo: false
  message: false
knitr:
  opts_chunk:
    fig.path: figures/
    fig.pos: H
title: "AAGI PPTX Presentation"
author: "Adam Sparks"
date: last-modified
date-format: long
---

```{r}
#| label: setup
#| include: false
#| message: false

allow_install <- isTRUE(as.logical(Sys.getenv(
  "AAGI_AUTO_INSTALL",
  unset = interactive()
)))

ensure_pkg <- function(pkg, github = NULL) {
  if (requireNamespace(pkg, quietly = TRUE)) {
    return(invisible(TRUE))
  }
  if (!allow_install) {
    stop(
      sprintf("Package '%s' is required but not installed.", pkg),
      call. = FALSE
    )
  }

  if (!requireNamespace("pak", quietly = TRUE)) {
    install.packages(
      "pak",
      repos = sprintf(
        "https://r-lib.github.io/p/pak/stable/%s/%s/%s",
        .Platform$pkgType,
        R.Version()$os,
        R.Version()$arch
      )
    )
  }
  pak::pak(github %||% pkg, dependencies = TRUE)
  invisible(TRUE)
}

# CRAN pkgs
for (p in c("ggplot2", "dplyr", "flextable", "gapminder", "gt")) {
  ensure_pkg(p)
}

# GitHub pkgs
ensure_pkg("AAGIThemes", github = "AAGI-AUS/AAGIThemes")
ensure_pkg("AAGIPalettes", github = "AAGI-AUS/AAGIPalettes")

suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(flextable)
  library(gapminder)
  library(gt)
  library(AAGIThemes)
  library(AAGIPalettes)
})
```

try(ggplot2::theme_set(AAGIThemes::theme_aagi()), silent = TRUE)
try(
  flextable::set_flextable_defaults(theme_fun = AAGIThemes::theme_ft_aagi),
  silent = TRUE
)
```

## An AAGI pptx Theme for Quarto

This Quarto extension allows you to create your slides using a theme that follows AAGI typography and colour styles and provides the official AAGI logo and cover image for the title slide.

## Bullet point

- Point 1
- Point 2

## Tables

For tables, we suggest pairing with the R package [{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) to provide AAGI themed tables using `theme_ft_aagi`, which offers more flexibility in formatting.

## Example

```{r}
#| label: tab-aagi
#| message: false

flex_tab <- flextable(
  head(airquality) |>
    mutate(`Month Name` = "May")
) |>
  theme_ft_aagi() |>
  autofit()

flex_tab
```

## Basic Figures

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming basic figures in R.

```{r}
#| label: graphics-figure
#| message: false

plot_aagi(pressure)
```

## Figures with {ggplot2}

[{AAGIThemes}](https://github.com/AAGI-AUS/AAGIThemes) also provides support for theming [{ggplot2}](https://ggplot2.tidyverse.org) outputs in R.

```{r}
#| label: ggplot2-figure
#| message: false

facet <- gapminder |>
  filter(continent != "Americas") |>
  group_by(continent, year) |>
  summarise(pop = sum(as.numeric(pop)), .groups = "drop")

col_values <- c(
  AAGIPalettes::colour_as_hex("AAGI Teal"),
  AAGIPalettes::colour_as_hex("AAGI Green"),
  AAGIPalettes::colour_as_hex("AAGI Yellow"),
  AAGIPalettes::colour_as_hex("AAGI Blue")
)

ggplot() +
  geom_area(data = facet, aes(x = year, y = pop, fill = continent)) +
  scale_fill_manual(values = col_values) +
  facet_wrap(~continent, ncol = 5) +
  scale_y_continuous(
    breaks = c(0, 2000000000, 4000000000),
    labels = c(0, "2bn", "4bn")
  ) +
  theme_aagi() +
  geom_hline(yintercept = 0, linewidth = 1, colour = "#474747") +
  theme(legend.position = "none", axis.text.x = element_blank()) +
  labs(
    title = "Asia's rapid growth",
    subtitle = "Population growth by continent, 1952–2007"
  )
```

## Slides With Columns

::::: columns
::: {.column width="50%"}
This is a column on the left.
:::

::: {.column width="50%"}
This is a column on the right.
:::
:::::

# Thank You
