---
format: aagi-pdf+short+report
params:
  # documents typically inherit params from _quarto.yml; you can override here
  report_title: "Example Short Report"
---

```{r}
#| include: false
source("_scripts/setup.R", local = TRUE)
```

# Section 

This template is designed for smaller ("one-page") AAGI reports. The AAGI logo and partners footer appear only on this first page.

You can colour text/tables/etc using the various AAGI palette colours. Use `\textcolor{aagiteal}{...}` for `\textcolor{aagiteal}{AAGI Teal}`, or `\textcolor{aagibrightgreen}{...}` for `\textcolor{aagibrightgreen}{AAGI Bright Green}`, for instance. @tbl-aagipalette shows the standard palette colours available for use.

::: {#tbl-aagipalette}
  \centering
  \begin{tabular}{|c | c | c | c |}
    \hline
    \cellcolor{aagibrightgreen}\texttt{aagibrightgreen} & %
    \cellcolor{aagiteal}\color{white}\texttt{aagiteal} & %
    \cellcolor{aagiblue}\texttt{aagiblue} & %
    \cellcolor{aagigreen}\texttt{aagigreen} \\
    \hline
    \cellcolor{aagiyellow}\texttt{aagiyellow} & %
    \cellcolor{aagiorange}\texttt{aagiorange} & %
    \cellcolor{aagiblack}\color{white}\texttt{aagiblack} & %
    \cellcolor{aagigrey}\texttt{aagigrey} \\
    \hline
  \end{tabular} 

The AAGI palette colours.
:::

## This is a subsection heading

This is an example of a reference [@blah]. References appear at the end of the report by default, after the last heading `# References` on the last line of this .Rmd file (but feel free to change the title to whatever you like).

\begin{note}
  {\bf\color{aagiteal!75!black} Example Note}\quad
  Use \verb|\begin{note}...\end{note}| to create coloured notes like this
  that stand out on the page.
\end{note}

Example R code, using the [{AAGIThemes}](https://aagi-aus.github.io/AAGIThemes/) package to produce Figure @fig-example1.

```{r}
#| label: fig-example1
#| fig-cap: "Here is a plot."
#| fig-height: 3
plot_aagi(pressure)
```

# Table example using {flextable}

```{r}
#| label: tbl-example
#| tbl-cap: "An example table using {flextable}."

ft <- flextable(head(airquality)) |>
  theme_ft_aagi() |>
  autofit()

ft
```

### This is a subsubsection heading

\lipsum[1-3]

And so on.

# Next Section

Add as many sections as needed.

# References
